Factoring with $n+2$ clean qubits and $n-1$ dirty qubits

### 2017-06-22 doc/paper.tex
Tweaking

A second way to reduce modular multiplication into (slightly) smaller operations could be with commutator control.
Note that the modular Fourier transform inverts the effect of modular multiplication: $QFT_{R} \cdot (\times K) \cdot QFT_R^{-1} = (\times K^{-1}) \pmod{R}$.
This has two useful high-level effects.
First, by applying the bimultiplication gate used in this paper twice, but inverting the effect on the ancilla register for the second application, we can build a proper modular multiplication gate that only affects a single register.
Second, we can use commutator control to move controls from the modular multiplication gate onto modular Fourier transform gates.
Assuming controlled modular QFTs can be performed with fewer ancillae than controlled modular multiplication, we could save a dirty ancilla when performing the modular multiplication by borrowing the control qubit.

>>>>

A second way to reduce modular multiplication into (slightly) smaller operations could be with commutator control.
Note that the modular Fourier transform inverts the effect of modular multiplication: $QFT_{R} \cdot (\times K \,\text{mod}\, R) \cdot QFT_R^{-1} = (\times K^{-1} \,\text{mod}\, R)$.
This has two useful high-level effects.
First, by applying the bimultiplication gate used in this paper twice, but inverting the effect on the ancilla register for the second application, we can build a proper modular multiplication gate that only affects a single register.
Second, we can use commutator control to move controls from the modular multiplication gate onto modular Fourier transform gates.
Assuming controlled modular QFTs can be performed with fewer ancillae than controlled modular multiplication, we could save a qubit when performing the modular multiplication by borrowing the control qubit.
